RadLib: a radiative property model library for combustion CFD

### 2021-05-04 manuscript/manuscript.tex
Finished overall and reviewer-based revisions to paper text. Updated soem of the figures for consistent presentation.

In combustion systems, this simplification is convenient because it makes radiation modeling easy to implement and computationally inexpensive. The vast majority of computational combustion research that considers radiation employs an optically thin approximation despite its limited applicability to combustion processes. Assuming optical thinness can predict the radiative behavior of small laboratory flames reasonably well, but in larger flame or industrial systems tends to overpredict radiative heat losses by 50\% or more and underpredicts flame temperatures by over 100$^{\circ}$C \citep{Modest_2016}.

@@

RadLib can also account for the radiative properties of soot in combustion environments. Soot particles are assumed to be unagglomerated spheres that absorb and emit radiation at all wavelengths such that their optical properties can be determined using the Rayleigh small particle limit. Radiation scattering may be neglected because unagglomerated soot particles in the Rayleigh regime are still small relative to the wavelength of infrared radiation in flames \cite{Brewster_1992,Solovjov_2001}. The spectral soot absorption coefficient is given by 
%
\begin{linenomath}
\begin{equation}
\label{e:soot1}
	\kappa_{s,\eta}=C_0 f_v \eta, \; \; \; C_0 = \frac{36\pi n k}{(n^2-k^2+2)^2+4n^2k^2},
\end{equation}
\end{linenomath}
%
where $n$ and $k$ are the real and imaginary parts of the soot complex index of refraction, respectively, and $f_v$ is the soot volume fraction \cite{Solovjov_2001,Modest_2013}. Various values for the refraction index have been proposed and applied \cite{Lee_1981,Stull_1960,Dalzell_1969,Howarth_1966,Chang_1990,Felske_1984,Williams_2007}. 
% INSERT FIGURE SHOWING DIFFERENT MODELS
RadLib uses the values $n=1.75$ and $k=1.03$ given in \cite{Williams_2007}, which result in a value of $C_0=7.03$, which is nearly the same as the value $C_0=7.0$ used in \cite{Solovjov_2001}. 
The Planck mean and Rosseland mean soot absorption coefficients are given in \cite{Modest_2013} as $\kappa_s=3.83f_vC_0T/C_2$ and $\kappa_s=3.60f_vC_0T/C_2$, respectively.
Due to the small difference between the coefficients in these two expressions, a mean value is suggested \cite{Felske_1977,Modest_2013}:
%
\begin{linenomath}
\begin{equation}
\label{e:soot2}
	\kappa_{soot}=3.72\frac{f_vC_0T}{C_2},
\end{equation}
\end{linenomath}
%
where $T$ is the temperature and $C_2=0.014388$ \si{m.K} is a Planck function constant \cite{Modest_2013}.

In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is added to the gas absorption coefficient. This gives $\kappa_s=1817f_vT$ \si{m^{-1}}.

In the WSGG model, Bordbar suggested incorporating soot as follows \cite{Bordbar_personal}. The soot absorption coefficient is similarly calculated from Eq.~\ref{e:soot2} but is then added to each of the gases separately. Because soot radiates across all wavelengths, its absorption coefficient is added to the values of all four gray gases and the clear gas. The gas weights $a_j$ are not changed. This model yeilds the expected behavior in the soot-only and gas-only limits.

The soot model used in the WSGG model can be applied to the RCSLW model as well. However, the formulation of the RCSLW model allows for a spectral soot treatment in the same manner as the gas species~\cite{Solovjov_2001}. Calculation of the soot ALBDF is facilitated by the simple $\eta$ dependence of $\kappa_{s,\eta}$ in Eq.~\ref{e:soot1}. The fraction of the black energy at wavenumbers below $\eta$ is computed directly using a series expansion from Chang and Rhee \cite{Chang_1984,Solovjov_2001}. The soot ALBDF is then included in the product of species ALBDFs to obtain the mixture ALBDF.

@@

RadLib is an object-oriented C++ class library that includes both C++ and Python interfaces. The RadLib package contains five subdirectories (upon initial download): \texttt{source} contains the RadLib source code; \texttt{build} contains installation files; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to generate code documentation with Doxygen (optional).

@@

RadLib installation is automated with CMake. First, navigate to the \texttt{build} directory. If the user requires an installation location other than the default \texttt{installed} directory, edit the \texttt{user\textunderscore config} file before running CMake. To compile the package, run the command \texttt{cmake -C user\textunderscore config ../source}. Upon successful completion, run \texttt{make} and then \texttt{make install} to complete the process. To use RadLib in C++ projects, include the generated C++ library file, located at \texttt{installled/lib/libradlib.a}, and/or header files, located in \texttt{installed/include}, according to the project's build scheme. To use RadLib in Python, update the system \texttt{PYTHONPATH} environment variable and import the module, named \texttt{pyrad}, into the project.

The interfaces, solver, and examples included with the library serve to demonstrate its use and validate the implementation and results. Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces. The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry. After creating a radiation object, users interact with RadLib through the \texttt{get\textunderscore k\textunderscore a()} function, which requires arguments corresponding to the system temperature; system pressure; species mass fractions for H$_2$O, CO$_2$, CO, and CH$_4$; soot volume fraction in units of parts per million (ppm), if applicable; and variables initialized to receive output values for the radiation absorption coefficients and their corresponding weights. For examples that illustrate how a user might interact with RadLib, refer to the \texttt{simple\textunderscore interface.cc} and \texttt{simple\textunderscore interface.py} example files located in the \texttt{examples/c++} and \texttt{examples/python} folders, respectively. For information about adding additional radiative property models to the RadLib library, please refer to the package documentation. 
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

@@

\section{Validation and Examples} \label{s:Examples}

Several examples are presented to illustrate the behavior of the models. The examples show heat flux $q$ or volumetric heat source $Q$ in one one-dimensional configurations with varying gas compositions and temperatures. We compare the PM, WSGG, and RCSLW models for each example. The examples correspond to those presented by Solvojov et al. \cite{Solovjov_2017} (S), Bordbar et al. \cite{Bordbar_2020} (B), Solovjov et~al. \cite{Solovjov_2001} (Sb), and the number of each example corresponds to the example number in the respective reference. A ray-tracing code is used to solve the radiative transport equation between two parallel plates. 
Table~\ref{t:examples} summarizes the cases. Example S1 is a hot slab next to a cold slab where the cold slab's thickness varies; Example S2 is isothermal with a thick slab of high CO$_2$ next to a thin slab of low CO$_2$ with variable thickness; Example S3 uses parabolic temperature and H$_2$O mole fraction profiles; Example S4 has a triangular temperature profile between equally-spaced isothermal regions; Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K; and Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $y_{CO2}=1-y_{H2O}$). Example Sb1 is a simple uniform temperature and composition profile with soot radiation. Each case is presented alongside the line-by-line (LBL) data presented in the references. 
%
\begin{table}
    \caption{Summary of example cases presented. S1-S5 are from \cite{Solovjov_2017}; B3 is from \cite{Bordbar_2020}; Sb1 is from \cite{Solovjov_2001}. All cases use $P=1$ atm and black walls.}
    \label{t:examples}
    \centering
    \resizebox{\textwidth}{!}{
    \begin{tabular}{c l l c c c}
        \hline
        Example & T(K)                           & $y_{H2O}$  $y_{CO2}$ (mole frac.)                     & L (m)   & $T_{walls}$ (K)\\
        \hline
        S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$     & $y_{CO2}=0.1$, $y_{H2O}=0.2$                          & 0.5-2.5 & cold, cold     \\
        S2 & T=1000                              & $y_{CO2}(x<0.5)=0.4$, $y_{CO2}(x>0.5)=0.1$            & 0.5-2.5 & cold, cold     \\
           &                                     & $y_{H2O}=0.0$                                         &         &                \\
        S3 & $T(x) = 4000x(L-x)/L^2 + 800$       & $y_{H2O}(x) = 0.8x(L-x)/L^2 + 0.12$                   & 1       & 800, 800       \\
           &                                     & $y_{CO2}=0$                                           &         &                \\
        S4 & middle third triangular to 2500     & $y_{H2O}=0.1$, $y_{CO2}=0$                            & 0.3     & 500, 500       \\
        S5 & $T(x) = 1000 + 500\cos(\pi x/L)$    & $y_{H2O}=0.1$, $y_{CO2}=0$                            & 2       & 1500, 500      \\
        B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$  & $y_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$         & 1       & 400, 400       \\
           &                                     & $y_{CO2}=1-y_{H2O}$                                   &         &                \\
        Sb1& $T = 1000$                          & $y_{H2O} = 0.2$, $y_{CO2}=0.1$, $y_{CO}=0.03$         & 1       & cold, cold     \\
        \hline
    \end{tabular}
    }
\end{table}
%
The examples are provided with the RadLib code and implemented in both C++ and Python. A Juptyer notebook is provided with the Python examples that runs the examples, displays the plots, and saves the plots to PDF files. Python and Cython versions of the one-dimensional solver \texttt{parallel\textunderscore planes.py} are provided for convenience.

These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these examples and their motivations can be found in their respective references. 
%TO DO address this:
While ommitted here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in \cite{Solovjov_2017,Bordbar_2020} such that these examples also serve as a validation of the implementation of the models.

Figure~\ref{f:examples} shows comparative results for the different radiation models for these cases. 
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        Example S1 & Example S2 \\
        \includegraphics[width=2.75 in]{fig_ex_1.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_2b.pdf} \\
        Example S3 & Example S4 \\
        \includegraphics[width=2.75 in]{fig_ex_3a.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_4a.pdf} \\
        Example S5 & Example B3 \\
        \includegraphics[width=2.75 in]{fig_ex_5b.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_6.pdf}
    \end{tabular}
    \caption{Results for examples summarized in Table~\ref{t:examples}.}
    \label{f:examples}
    \end{center}
\end{figure}
%
In general, the PM model performs poorly compared to the WSSGG and RCSLW models. A notable exception is Example S4. In Example S2, the PM $q(L)/\sigma T^4$ is off scale at an essentially constant at a value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, giving optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively, which are relatively small compared to the isothermal domain size greater than 0.5 m. Example S5 omits the PM model to more clearly show the behavior of the WSGG and RCSLW models. For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 kW/m$^3$ at $x=0$ to a peak of 200 kW/m$^3$ at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m. In all examples, four gray ($n=4$) and one clear gas are computed for the RCSLW models to give a consistent comparison to the WSGG model. Example S5 shows the sensitivity of the RCSLW model to the number of gases used. The difference between $n=2$ and $n=8$ is very small for all examples shwon, except for Example S2. When $n$ is increased from four to eight for that example the RCSLW model improves to show nearly perfect agreement with the LBL data.
In all Examples, the RCSLW model is initialized using the mean temperature and composition on the domain. In Example S5, the RCSLW model converges to the LBL solution when the model is initialized using the maximum temperature instead of the average temperature.

Figure~\ref{f:exSb1} shows the results from Example Sb1, which includes soot radiation. Results for three values of the soot volume fraction are shown. Both the WSGG and RCSLW models perform very well for each case. 
%
\begin{figure}
    \begin{center}
        \includegraphics[width=5.5 in]{fig_ex_Sb1.pdf}
    \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
    \label{f:exSb1}
    \end{center}
\end{figure}
%

@@

\section{Discussion} \label{s:impact}

%Note that we are presenting and not evaluating the models and make no claims as to causes of the results presented in the previous section. Several of the example cases deviate from the expected behavior (i.e. S2, S4). Also note that the PM and WSGG models are mostly empirical and contain very little representative physics, which can cause them to behave unpredictably in parameter ranges outside of those for which the models were specifically developed. If we look at Bordbar's paper, WSGG looks really good, but Example S4 gives us behavior we don't expect---WSGG performs very poorly. We don't know why, and we don't intend to explain it, but this is a good illustration of the fact that sometimes models need to be tested independently before application to a specific project. Sometimes a model that seems perfect may not be for your case, and RadLib is a good tool for investigating things like that.

Radiative heat transfer models are historically difficult to implement in CFD codes due to their complexity and high computational costs. Neglecting radiation or using simple models like the Planck Mean model is adequate for some cases with simple geometry or limited chemical heat release, which are usually associated with optical thinness and low rates of radiative reabsorption, but most combustion simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results. In such cases, radiation models that are incorrectly implemented or inappropriate for the simulation parameters can become additional sources of error that may be extremely difficult to separate from existing sources or error. Currently, researchers that require detailed radiation modeling must code and validate it themselves at the expense of valuable research time and funding.

RadLib makes researchers' work easier by consolidating various approaches into a modular library of interchangeable, prevalidated radiation models. Additionally, RadLib's modular framework can also accommodate new models, allowing researchers to compare new or existing models with very little overhead. Sometimes, it is not clear which radiation model may be the best fit for a particular simulation. When simulations are especially complex or computationally expensive, researchers may have to extrapolate from theory and literature to choose an appropriate radiation model rather than testing for their specific case. RadLib is designed to ease both of these obstacles by facilitating comparison between radiation models through a common interface and providing a practical means of testing various models without the restriction of prespecified geometry or case parameters. With RadLib, researchers can put more of their time and effort into useful results rather than code or model development.

Currently, RadLib is only used within the authors' research group, where it is applied to combustion CFD simulations using the One-Dimensional Turbulence (ODT) model \cite{Stephens_2020}, but its design and structure as a C++ library allows it to be incorporated easily into existing codes. It can be applied to  research questions in various other fields involving radiative heat transfer as well, including energy engineering or atmospheric and climate sciences. Radiation is a universal phenomenon, and RadLib can assist researchers in many areas with systems and processes that involve heat transfer.

@@

A comparison was made of the computational cost of the current models implemented. Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7. Figure~\ref{f:cost}a shows the cost to compute the gas properties $k$ and $a$. This was done by timing the C++ code execution to evaluate the gas properties one million times in a loop and then averaging the results. The figure shows times normalized by the time for the WSGG model, which required 8.0E-7~s. The costs of the models, relative to WSGG, is 0.098, 1.9, 4.9, 9.4, and 18, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively. The cost of the RCSLW model is very nearly proportional to the number of gray gases considered.
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        (a) & (b) \\
        \includegraphics[width=2.75 in]{fig_getka_c++.pdf} &
        \includegraphics[width=2.75 in]{fig_exS3_c++.pdf}
    \end{tabular}
    \caption{Computational cost to evaluate gas properties (a) and to run Example S3 (b). Results are normalized by the cost of the WSSG model.}
    \label{f:cost}
    \end{center}
\end{figure}
%

Figure~\ref{f:cost}b shows the cost to evaluate Example S3. 
In this case the costs of the models, relative to WSGG, is approximately 0.75, 1.1, 1.4, 1.9, and 2.9, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively. Here, the WSGG model took 0.0079 s. In running Example S3, the costs of the various models are much more similar than in evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations. In the results presented, only the cost of evaluating the solution was included; initialization and input/output costs were neglected.

>>>>

In combustion systems, this simplification is convenient because it makes radiation modeling easy to implement and computationally inexpensive. The vast majority of computational combustion research that considers radiation employs an optically thin approximation despite its limited applicability to combustion processes. Assuming optical thinness can predict the radiative behavior of small laboratory flames reasonably well, but in larger flames or industrial systems tends to overpredict radiative heat losses by 50\% or more and underpredicts flame temperatures by over 100$^{\circ}$C \citep{Modest_2016}.

@@

RadLib can also account for the radiative properties of soot in gaseous combustion environments. Soot particles are assumed to be unagglomerated spheres that absorb and emit radiation at all wavelengths such that their optical properties can be determined using the Rayleigh small particle limit. This assumption implies that radiation scattering may be neglected because unagglomerated soot particles in the Rayleigh regime are still small relative to the wavelength of infrared radiation in flames \cite{Brewster_1992,Solovjov_2001}. The spectral soot absorption coefficient is given by 
%
\begin{linenomath}
\begin{equation}
\label{e:soot1}
	\kappa_{s,\eta}=C_0 f_v \eta, \; \; \; C_0 = \frac{36\pi n k}{(n^2-k^2+2)^2+4n^2k^2},
\end{equation}
\end{linenomath}
%
where $n$ and $k$ are the real and imaginary parts of the soot complex index of refraction, respectively, and $f_v$ is the soot volume fraction \cite{Solovjov_2001,Modest_2013}. Various values for the refraction index have been proposed and applied \cite{Lee_1981,Stull_1960,Dalzell_1969,Howarth_1966,Chang_1990,Felske_1984,Williams_2007}. 
RadLib uses the most current values in the literature: $n=1.75$ and $k=1.03$ \cite{Williams_2007}, resulting in a value of $C_0=7.03$, which is nearly the same as the value of $C_0=7.0$ used by Solovjov and Webb \cite{Solovjov_2001} to study radiative transfer in sooty gas mixtures. 
The Planck mean and Rosseland mean soot absorption coefficients are given in \cite{Modest_2013} as $\kappa_s=3.83f_vC_0T/C_2$ and $\kappa_s=3.60f_vC_0T/C_2$, respectively.
Due to the small difference between the coefficients in these two expressions, the mean value suggested by \cite{Modest_2013,Felske_1977} is used in RadLib's soot calculations:
%
\begin{linenomath}
\begin{equation}
\label{e:soot2}
	\kappa_{soot}=3.72\frac{f_vC_0T}{C_2},
\end{equation}
\end{linenomath}
%
where $T$ is the temperature and $C_2=0.014388$ \si{m.K} is a Planck function constant \cite{Modest_2013}.

In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient. Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ \si{m^{-1}}.

In the WSGG model, the soot absorption coefficient is also computed using Eq.~\ref{e:soot2} but then added to each of the gray gases separately \cite{Bordbar_personal}. Because soot radiates across all wavelengths, its absorption coefficient is added to the value of the clear gas in addition to the values of all four gray gases. The gas weights $a_j$ are not changed. This model yields the expected behavior in the soot-only and gas-only limits.

The WSGG soot treatment can be applied to the RCSLW model as well. Alternatively, the RCSLW model's formulation permits a spectral soot treatment in the same manner as the gas species~\cite{Solovjov_2001}. Calculation of the soot ALBDF is facilitated by the simple $\eta$ dependence of $\kappa_{s,\eta}$ in Eq.~\ref{e:soot1}. The fraction of total blackbody emission at wavenumbers below $\eta$ is computed directly using a series expansion presented by Chang and Rhee \cite{Chang_1984}. The soot ALBDF is then included in the product of species ALBDFs to obtain the mixture ALBDF, as in Eq.~\ref{e:multiF}.

@@

RadLib is an object-oriented C++ class library that includes both C++ and Python interfaces. Upon initial download, the RadLib package contains five subdirectories: \texttt{src} contains the RadLib source code; \texttt{build} contains installation files; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to optionally generate code documentation with Doxygen. An additional directory, \texttt{installed}, is created and populated with RadLib's executables and header files during installation if no other installation location is specified.

@@

RadLib installation is automated with CMake from within the \texttt{build} directory. If the user requires an installation location other than the default \texttt{installed} directory, edit the "Project Options" section of \texttt{build/CMakeLists.txt} file before running CMake. First, configure CMake by running the command \texttt{cmake .} from within the \texttt{build} directory. Upon successful completion, run \texttt{make} to compile the library and then \texttt{make install} to install it. To use RadLib in C++ projects, include the generated C++ library file, located at \texttt{installled/lib/libradlib.a}, and/or header files, located in \texttt{installed/include}, according to the project's build scheme. Installation also generates a relocatable RadLib package, located at \texttt{build/cmake/radlib/radlib.cmake}, for downstream usage. To use RadLib in Python, update the system \texttt{PYTHONPATH} environment variable and import the module, named \texttt{pyrad}, into the project.

The interfaces, solver, and examples included with the library serve to demonstrate its use and validate the implementation and results. Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces. The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular case geometry. After creating a radiation object, users interact with RadLib through the \texttt{get\textunderscore k\textunderscore a()} function, which requires arguments corresponding to the system temperature; system pressure; species mass fractions for H$_2$O, CO$_2$, CO, and CH$_4$; soot volume fraction in units of parts per million (ppm), if applicable; and variables initialized to receive output values for the radiation absorption coefficients and their corresponding weights. For examples that illustrate how a user might interact with RadLib, refer to the \texttt{simple\textunderscore interface.cc} and \texttt{simple\textunderscore interface.py} example files located in the \texttt{examples/c++} and \texttt{examples/python} folders, respectively. For information about adding additional radiative property models to the RadLib library, please refer to the package documentation. 
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

@@

\section{Examples} \label{s:Examples}

The RadLib package includes several example cases that illustrate the behavior of the models and interfaces. The examples compare the PM, WSGG, and RCSLW models via output heat flux $q$ or volumetric heat source $Q$ in one-dimensional configurations with varying gas compositions and temperatures. 
The RTE is solved between two parallel plates with a ray-tracing code, included in the RadLib package. Each case's results is presented alongside the line-by-line (LBL) data from its respective reference.

Table~\ref{t:examples} summarizes the example cases. Each case is labeled according to its source---Solvojov et al. \cite{Solovjov_2017} (S), Bordbar et al. \cite{Bordbar_2020} (B), or Solovjov et~al. \cite{Solovjov_2001} (Sb)---and the number of each example corresponds to the example number in its respective reference. Each example case consists of one or more gas layers ("slabs") bounded by black walls. 
Example S1 consists of two adjacent gas layers with identical species compositions: one hot layer of constant thickness and one cold layer of varying thickness. 
In Example S2, the two gas layers are isothermal but differ in the value of the \ce{CO2} mole fraction, where the layer thickness of the "thin" slab (with the smaller \ce{CO2} mole fraction) varies.
Example S3 applies parabolic temperature and \ce{H2O} mole fraction profiles across a single gas layer. 
Example S4 divides the gas into three equally-spaced layers and applies a triangular temperature profile to the middle layer and a constant temperature to the two outer layers.
Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K applied to a single gas layer of constant species composition.
Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $y_{CO2}=1-y_{H2O}$). 
Example Sb1 consists of a single gas with a uniform temperature and composition profile and soot radiation. 
%
\begin{table}
    \caption{Summary of example cases. All cases use $P=1$ atm and black walls.}
    \label{t:examples}
    \centering
    \resizebox{\textwidth}{!}{
    \begin{tabular}{c l l c c c c}
        \hline
        Example & T(K)                          & $y_{H2O}$  $y_{CO2}$ (mole frac.)               & L (m)   & $T_{walls}$ (K) & Ref.\\
        \hline
        S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$    & $y_{CO2}=0.1$, $y_{H2O}=0.2$                    & 0.5-2.5 & cold, cold	& \cite{Solovjov_2017}     \\
        S2 & T=1000                             & $y_{CO2}(x<0.5)=0.4$, $y_{CO2}(x>0.5)=0.1$      & 0.5-2.5 & cold, cold & \cite{Solovjov_2017}    \\
           &                                    & $y_{H2O}=0.0$                                   &         &                \\
        S3 & $T(x) = 4000x(L-x)/L^2 + 800$      & $y_{H2O}(x) = 0.8x(L-x)/L^2 + 0.12$             & 1       & 800, 800 & \cite{Solovjov_2017}      \\
           &                                    & $y_{CO2}=0$                                     &         &                \\
        S4 & middle third triangular to 2500    & $y_{H2O}=0.1$, $y_{CO2}=0$                      & 0.3     & 500, 500 & \cite{Solovjov_2017}      \\
        S5 & $T(x) = 1000 + 500\cos(\pi x/L)$ 	 & $y_{H2O}=0.1$, $y_{CO2}=0$                      & 2       & 1500, 500 & \cite{Solovjov_2017}     \\
        B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$ & $y_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$	& 1       & 400, 400 & \cite{Bordbar_2020}      \\
           &                                    & $y_{CO2}=1-y_{H2O}$                             	&         &                \\
        Sb1& $T = 1000$                         & $y_{H2O} = 0.2$, $y_{CO2}=0.1$, $y_{CO}=0.03$   	& 1       & cold, cold & \cite{Solovjov_2001}    \\
        \hline
    \end{tabular}
    }
\end{table}
%

The examples are provided with the RadLib code and implemented in both C++ and Python. A Juptyer notebook is provided with the Python examples that runs the examples, displays the plots, and saves the plots to PDF files. Python and Cython versions of the one-dimensional solver \texttt{parallel\textunderscore planes.py} are provided for convenience.

These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these examples and their motivations can be found in their respective references. Comparison of these results to the LBL data and to the results presented in the source references also serves as a validation of RadLib's implementation of the WSGG and RCSLW models.

@@

\section{Results and Discussion} \label{s:discussion}

Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}. In all examples, the RCSLW model data is computed using four gray gases ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Example S5, in which the number of gray gases in the RCSLW model is varied. The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature instead. 
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        Example S1 & Example S2 \\
        \includegraphics[width=2.75 in]{fig_ex_S1.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_S2b.pdf} \\
        Example S3 & Example S4 \\
        \includegraphics[width=2.75 in]{fig_ex_S3a.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_S4a.pdf} \\
        Example S5 & Example B3 \\
        \includegraphics[width=2.75 in]{fig_ex_S5c.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_B3.pdf}
    \end{tabular}
    \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}.}
    \label{f:examples}
    \end{center}
\end{figure}
%
\begin{figure}
    \begin{center}
        \includegraphics[width=5.5 in]{fig_ex_Sb1.pdf}
    \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
    \label{f:exSb1}
    \end{center}
\end{figure}
%

In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data. The data for Examples S1, S3, and B3 show that the PM model tends to exaggerate the trends displayed by the other models; this is also true of Example S4, though the effect is somewhat overshadowed by the WSGG model results. The PM data mimics the shape of the other curves in Example S5 as well, but with such greatly exaggerated peaks and valleys that its data was omitted from the plot to more clearly display the behavior of the WSGG and RCSLW models; for the PM model in Example S5, $Q$ varies from around -80 kW/m$^3$ at $x=0$ to a peak of 200 kW/m$^3$ at x=$1.5$ m and drops to 100 kW/m$^3$ at $x=2$ m. 
In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively. These values are small compared to the domain sizes considered in Example S2, which coincides with the PM model's use of the optically thin approximation, but the high error in its predictions of radiative heat flux relative to the LBL data indicates that neither the optically thin approximation nor absorption coefficients calculated with this model are accurate for this case. Example S3 is the clearest illustration of the PM model's deficiencies as discussed in Section~\ref{s:planckmean}: the PM model severely overpredicts radiative heat loss at the high temperatures that characterize most combustion processes.

The WSGG model gives somewhat accurate but inconsistent results for the example cases considered here. In Examples S1, S3, S5, B3, and Sb1, it behaves as expected, producing results that are closer to the LBL data than those produced by the PM model but fall short of the RCSLW model's level of accuracy. In general, the WSGG model appears to perform best at intermediate temperatures and deviates from the desired behavior at boundary conditions, but this is not universal. For example, the WSGG model shows uncharacteristically high accuracy in Example S2; its results with four gray gases are comparable in accuracy to the RCSLW model's performance using eight or more gray gases. In contrast, the WSGG model performs exceptionally poorly in Example S4, in which it deviates from the LBL data by nearly an order of magnitude at its largest. 
The WSGG model, alongside with the PM model, is primarily empirical and contains little to no representative physics, which could explain the unexpected behavior in Examples S2 and S4. Given that all of the example cases use parameters within those specified for the WSGG model in the literature \cite{Bordbar_2014,Bordbar_2020}, neither anomalous result has an obvious source. While we cannot offer an explanation for the WSGG model's inconsistent performance, it serves to underscore the importance of individual model validation on a case-by-case basis, a task potentially made easier with tools like RadLib.

The RCSLW model displays the most accurate results of the three implemented property models when compared to LBL data, capturing the relevant trends without exaggerating them. It is, however, the most difficult of the three models to implement and requires either correlated or tabulated spectral data to draw from. The RCSLW model can also be sensitive to the number of gray gases used, illustrated in Figure~\ref{f:examples} by Examples S2 and S5. The difference in accuracy between $n=2$ and $n=8$ gray gases is very small for all of the example cases and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data. Example S2 shows the most prominent variations in predicted radiative heat flux based on changes in the number of gray gases, improving drastically in agreement to the LBL data with the addition of just four gray gases. RCSLW model convergence can also vary with the value of the chosen reference temperature; in Example S5, for instance, the RCSLW model converges to the LBL data if it is initialized with the maximum rather than the average temperature on the domain. When treated properly, however, the RCSLW model provides the most accurate results of all of the radiation property models considered here.

Figure~\ref{f:exSb1} shows the results from Example Sb1, which considers three magnitudes of the soot volume fraction in addition to the radiating gas. Both the WSGG and RCSLW models perform accurately in all three cases, but the PM model displays significant deviations from the LBL data. In sooting flames, soot acts as a significant source and sink of radiation, and its radiative properties differ significantly from those of the participating gaseous species. Soot reactions and transport are both sensitive to and strongly influence local variations in flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes. The agreement produced by RadLib's approach to soot radiation in Example Sb1 is an encouraging step toward accurate, detailed treatment of soot's radiative properties in complex combustion simulations.

@@

In addition to comparing model attributes and performance, we evaluated and compared the computational cost of the implemented radiation property models. 
Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7; the results, normalized by the cost of the WSGG model, are summarized in Figure~\ref{f:cost}.

Figure~\ref{f:cost}a displays the relative cost to compute the gas properties $k$ and $a$, represented by the time required to execute the C++ function \texttt{get\textunderscore k\textunderscore a()}, averaged over one million evaluations. The results for each model are normalized by the WSGG model, which required an average of 8.0E-7~s. Relative to the WSGG model, the cost to evaluate the gas properties with the PM model was 0.098. The RCSLW model was evaluated with $n=1$, 2, 4, and 8 gray gases, which resulted in relative costs of 1.9, 4.9, 9.4, and 18, respectively. The cost of the RCSLW model is very nearly proportional to the number of gray gases considered.
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        (a) & (b) \\
        \includegraphics[width=2.75 in]{fig_getka_c++.pdf} &
        \includegraphics[width=2.75 in]{fig_exS3_c++.pdf}
    \end{tabular}
    \caption{Relative computational cost to (a) evaluate gas properties only and (b) run Example S3, including the ray-tracing solver. Results are normalized by the cost of the WSSG model for each case.}
    \label{f:cost}
    \end{center}
\end{figure}
%

Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties and solution of the RTE using the provided ray-tracing solver. In the results presented, only the cost of evaluating the solution was included; initialization and input/output costs were neglected.
Relative to the WSGG model, which required 0.0079 s, the model costs for the PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively. In running Example S3, the model costs vary much less than when evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations.
